%-------------------------
% Adapted from a template by Jake Gutierrez
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Matthew Crown} \\ \vspace{4pt}
    \small +44 7736 753863 $|$ \href{mailto:matthewcrown@hotmail.co.uk}{\underline{matthewcrown@hotmail.co.uk}} $|$ 
    \href{https://m-crown.github.io}{\underline{m-crown.github.io}} $|$
    \href{https://linkedin.com/in/matthew-crown}{\underline{linkedin.com/in/matthew-crown}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northumbria University}{Newcastle, UK}
      {PhD in Bioinformatics (submitted)}{Sep. 2020 -- Oct. 2024}
      \resumeItemListStart
        \resumeItem{Thesis Title: "Global, viral and protein scale functional annotation tools for -omics and structural bioinformatics.". See projects section for more information on projects developed during PhD.}
      \resumeItemListEnd
    \resumeSubheading
      {Newcastle University}{Newcastle, UK}
      {BSc. (Hons) Biochemistry}{Sep. 2016 -- Jun. 2020}
      \resumeItemListStart
        \resumeItem{Dissertation title: “Proteomic analysis of the E3-ubiquitin ligase
        DTX3L interactome”}
        \resumeItem{Graduated with First Class Honours and awarded the Gus Lienhard Prize for Biochemistry.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Employment and Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Senior Research Assistant}{Newcastle, UK}
      {COVID19 Sequencing Group, Northumbria University}{Oct. 2021 -- Sep. 2022}
      \resumeItemListStart
        \resumeItem{Part of the COVID19 Genomics Consortium (COG-UK) Sequencing efforts at Northumbria University and developed a novel structural and functional annotation tool for SARS-CoV-2 proteins (see Projects).}
        \resumeItem{Undertook routine analysis of SARS-CoV-2 sequencing data as part of the sequencing efforts, including running and troubleshooting Nextflow pipelines, handling sensitive metadata linkage, and developing SOPs.}
      \resumeItemListEnd
    \resumeSubheading
      {Industrial Placement}{Stevenage, UK}
      {Exploratory Biomarker Assay Group, GlaxoSmithKline}{Sep. 2018 -- Aug. 2019}
      \resumeItemListStart
        \resumeItem{1-year industrial placement. The focus of work was development and optimisation of assays to support preclinical/clinical safety and efficacy studies of large and small molecule drugs.}
        \resumeItem{Utilised commercial immunoassay and flow cytometry platforms and performed downstream data analysis.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Research Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{AlphaCognate} $|$ \emph{Python, GEMMI, Nextflow, Git}}{May. 2024 -- Present}
        \resumeItemListStart
          \resumeItem{Developed a tool for transplantation of cognate ligands to predicted protein structures, which integrates annotation data from ProCogGraph (see below) through a Snakemake pipeline, and uses the GEMMI package for structural superposition of predicted and known protein structures.}
        \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{ProCogGraph} $|$ \emph{neo4j, Python, RDKit, Arpeggio, Nextflow, Git}}{Jan. 2023 -- Jun. 2024}
          \resumeItemListStart
            \resumeItem{Developed a graph database (neo4j) of enzyme domain-ligand interactions and cognate ligand mapping.}
            \resumeItem{The database is built using a Nextflow pipeline, and integrates chemoinformatics ligand similarity matching and protein contact analysis.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{OMEinfo} $|$ \emph{Docker, Python, Rasterio, Rio-Cogeo, Git}}{Jan. 2023 -- Sep. 2023}
          \resumeItemListStart
            \resumeItem{Developed a metadata annotation tool to automatically and consistently annotate locations with geospatial features, which allows non-expert users to integrate specialist geospatial data formats (GeoTIFF) into their metadata.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{SPEAR} $|$ \emph{Python, Snakemake, minimap2, Plotly, Bash, Git}}{Oct. 2021 -- Sep. 2022}
          \resumeItemListStart
            \resumeItem{Developed a pipeline for rapid structural and functional annotation of SARS-CoV-2 proteins, including antibody escape potential and conformational dynamics.}
            \resumeItem{The tool includes a report feature which allows easy comprehension of complex structural/functional features of the virus for non-expert decision makers.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
For a full list of publications, see my Google Scholar profile: \href{https://scholar.google.com/citations?user=b8OKEYcAAAAJ&hl=en&oi=ao}{\underline{Google Scholar}}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, R, Bash, Cypher, HTML/CSS} \\
     \textbf{Reproducible Workflow \& DevOps Tools}{: Snakemake, Nextflow, Git, Docker} \\
     \textbf{Bioinformatics Tools}{: Biopython, GEMMI, RDKit, Pymol, } \\
     \textbf{Generic Tools and Libraries}{: neo4j, pandas, NumPy, Matplotlib, scikit-learn}
     
    }}
 \end{itemize}


%-------------------------------------------
%
%-----------PERSONAL-----------
\section{Personal Interests}
\begin{flushleft}
Outside of work, I am a keen runner, having recently completed my first Great North Run for charity. I also enjoy the physical challenge and problem solving of bouldering. Whilst my work focusses on bioinformatics, I also have a passion for technology and enjoy learning about and tinkering with the latest new hardware and software.
\end{flushleft}

%-------------------------------------------
\end{document}